\cvsection{Honors and Awards (Selected)}

\begin{awardentries}
    \awardentry{\textbf{Gold Medal}, 2019 China Collegiate Computing Contest - Group Programming Ladder Tournament}{Mar. 2019}
    \awardentry{\textbf{Excellent Student Scholarship}, University of Electronic Science and Technology of China}{Dec. 2018}
    % \awardentry{\textbf{The 2018 ACM-ICPC \textcolor{emphred}{Asia-East Continent Final} Silver Medal}}{Nov. 2018}
    % \awardentry{\textbf{The 2018 ACM-ICPC Asia Regional Contest (Xuzhou Site) Silver Medal}}{Oct. 2018}
    % \awardentry{\textbf{The 2018 ICPC China SiChuan Provincial Programming Contest Gold Medal}}{Jun. 2018}
    % \awardentry{\textbf{2018 China Collegiate Programming Contest - National Invitational Contest (Hunan) Silver Medal}}{May 2018}
    % \awardentry{\textbf{2018 COMAP's Mathematical Contest in Modeling® (MCM) Honorable Mention} (Top 40\%)}{Feb. 2018}
    % \awardentry{\textbf{IEEEXtreme Programming Competition 11.0 Global 81st Place} (Top 4\%)}{Oct. 2017}
    % \awardentry{\textbf{The 2017 ACM-ICPC Asia Regional Contest (Xi'an Site) Bronze Medal}}{Oct. 2017}
    % \awardentry{\textbf{Silver Medal}, The 2018 ACM-ICPC \textcolor{emphred}{Asia-East Continent Final}}{Nov. 2018}
    \textcolor{emphred}{\awardentry{\textbf{Silver Medal}, The 2018 ACM-ICPC Asia-East Continent Final}{Nov. 2018}}
    \awardentry{\textbf{Silver Medal}, The 2018 ACM-ICPC Asia Regional Contest (Xuzhou Site)}{Oct. 2018}
    \awardentry{\textbf{Gold Medal}, The 2018 ICPC China SiChuan Provincial Programming Contest}{Jun. 2018}
    \awardentry{\textbf{Silver Medal}, 2018 China Collegiate Programming Contest - National Invitational Contest (Hunan)}{May 2018}
    \awardentry{\textbf{Gold Medal}, 2018 China Collegiate Computing Contest - Group Programming Ladder Tournament}{Mar. 2018}
    \awardentry{\textbf{Honorable Mention} (Top 40\%), 2018 COMAP's Mathematical Contest in Modeling® (MCM)}{Feb. 2018}
    \awardentry{\textbf{First Prize} (Only one team), 2018 UESTC's Mathematical Contest in Modeling}{Dec. 2017}
    \awardentry{\textbf{Model Student Scholarship}, University of Electronic Science and Technology of China}{Dec. 2017}
    \awardentry{\textbf{Global 81st Place} (Top 4\%), IEEEXtreme Programming Competition 11.0}{Oct. 2017}
    \awardentry{\textbf{Bronze Medal}, The 2017 ACM-ICPC Asia Regional Contest (Xi'an Site)}{Oct. 2017}
\end{awardentries}

\endinput